### 2012-11-22 inst/examples/mult_uncertainty_test.Rmd
Larger (log-normal in all variables) noise, weirder results.

```{r plotting, include=FALSE}
theme_publish <- theme_set(theme_bw(14))
theme_publish <- theme_update(
        # panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
        legend.title=element_blank(), 
        panel.background = element_rect(fill = "transparent",colour = NA), 
        plot.background = element_rect(fill = "transparent",colour = NA))
```

@@

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){
          out[1] <- 1   
        } else {
         out <- pdfn(x_grid, mu, sigma_g)
        }
        out/sum(out)
      }))
    })

    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      ## q can often exceed y, if fishing is free, there might be more x than you think.  
      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * t(M) %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

sigma_g=0.1
````

@@

```{r noisetypes}
g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.1, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.1), pdfn=pdfn)  
```

>>>>

```{r plotting, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
opts_chunk$set(dev.args=list(bg="transparent"))
```

@@

    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        # Handle special cases
        if(snap_to_grid(mu,x_grid)==0){ # 
          out[1] <- 1   
        } else {
         out <- pdfn(x_grid, mu, sigma_g)
        }
        out/sum(out)
      }))
    })

    # n_y by n_x, given y %*% n_x by n_h %*% n_h by n_q, given q
    Ep <- M %*% P %*% t(I)
    V <- Ep
    for(t in 1:Tmax){
      D[,(Tmax-t+1)] <- apply(V, 1, which.max) 
      ## q can often exceed y, if fishing is free, there might be more x than you think.  
      #if(any(pmin(D[,(Tmax-t+1)], 1:n_h) !=  D[,(Tmax-t+1)])) stop()
      #v_t <- sapply(1:n_h, function(i) V[i,D[i,(Tmax-t+1)]]) # Look-up value given by which.max
      v_t <- apply(V, 1, max) # vector of current values 
      V <- sapply(1:n_h, function(j){ # updated value matrix
        Ep[,j] + (1-delta) * M %*% F[[j]] %*% v_t
      })
    }
    list(D=D, M=M, I=I, P=P, Ep=Ep, V=V, F=F)
}

@@

sigma_g=0.3
````

@@

```{r noisetypes}
g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.03, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
```
